edo_for_manuscript

### 2025-04-16 code/eda-code/eda_for_manuscript.qmd
Part 5 Commit 1

```{r}
#Path to data. Note the use of the here() package and not absolute paths
data_location <- here::here("data","processed-data","project_data.rds")
#load data
project_data <- readRDS(data_location)
```

@@

```{r}
#histogram of differnce in coverage
outcome_hist <- ggplot(project_data, aes(x = coverage_diff)) +
  geom_histogram(binwidth = 5, fill = "skyblue", color = "black") +
  labs(
    x = "Difference in HPV vaccination coverage from 2022 to 2019",
    y = "Count"
  )

@@

#### Creating "Table 1" to show the distribution of each characteristic
```{r}
  table1 <- project_data %>% dplyr::select(-CODE, -CODE2, -Country, -year_covid) %>% #Reordering the variables into the order I want displayed in the table
  dplyr::select(coverage_2022, coverage_2019, coverage_diff, Cumulative_case_rate, Cumulative_death_rate, HPV_NATIONAL_SCHEDULE, HPV_YEAR_INTRODUCTION, HPV_PRIM_DELIV_STRATEGY, HPV_SEX, doses_rec, WHO_REGION, WB_INCOME, total_pop,  total_pop, pop_density, median_age, pop_growth_rate, fertility_rate, death_rate, life_expect, migration) %>%
  tbl_summary(
    type = all_continuous() ~ "continuous2",
    statistic = list(   #Setting the statistics to calculate
      all_continuous() ~ c(
      "{mean} ({sd})",
      "{median} ({p25}, {p75})"
    ),
      all_categorical() ~ "{n} / {N} ({p}%)"),
    digits = list(   #Setting number of decimal places for each variable
      coverage_2022 ~ 1,
      coverage_2019 ~ 1,
      coverage_diff ~ 1,
      Cumulative_case_rate ~ 1,
      Cumulative_death_rate ~ 1,
      HPV_YEAR_INTRODUCTION ~ function(x) sprintf("%.0f", x),
      total_pop ~ 1,
      pop_density ~ 1,
      median_age ~ 1,
      pop_growth_rate ~ 1,
      fertility_rate ~ 1,
      death_rate ~ 1,
      life_expect ~ 1,
      migration ~ 1
    )) %>%
  modify_header(
    stat_0 = "**n/N (%), mean (sd), or median (IQR),** N = {n}") %>%
  modify_footnote(all_stat_cols() ~ NA) %>%
  modify_table_styling(
    columns = label,    # left aligning "label" column
    align = "left"
  ) 
# modify_header(stat0~ "**n/N (%), mean (sd), or median (IQR),**\n N = {n}")

@@

```{r}
#This is creating the combined table 1 that can be used to pull numbers from 
# Process the data and create a summary table using dplyr
word_list <- c("coverage_2022", "coverage_2019", "coverage_diff", "Cumulative_case_rate", 
    "Cumulative_death_rate", "HPV_NATIONAL_SCHEDULE", "HPV_YEAR_INTRODUCTION", 
    "HPV_PRIM_DELIV_STRATEGY", "HPV_SEX", "doses_rec", "WHO_REGION", "WB_INCOME", 
    "total_pop", "pop_density", "median_age", "pop_growth_rate", "fertility_rate", 
    "death_rate", "life_expect", "migration")
table1_prelim <- project_data %>%
  dplyr::select(-CODE, -CODE2, -Country, -year_covid) %>%
  dplyr::select(
    coverage_2022, coverage_2019, coverage_diff, Cumulative_case_rate, 
    Cumulative_death_rate, HPV_NATIONAL_SCHEDULE, HPV_YEAR_INTRODUCTION, 
    HPV_PRIM_DELIV_STRATEGY, HPV_SEX, doses_rec, WHO_REGION, WB_INCOME, 
    total_pop, pop_density, median_age, pop_growth_rate, fertility_rate, 
    death_rate, life_expect, migration
  ) %>%
  tbl_summary(
    type = all_continuous() ~ "continuous2",
    statistic = list(
      all_continuous() ~ c("{mean} ({sd})", "{median} ({p25}, {p75})"),
      all_categorical() ~ "{n} / {N} ({p}%)"
    ),
    digits = list(
      coverage_2022 ~ 1,
      coverage_2019 ~ 1,
      coverage_diff ~ 1,
      Cumulative_case_rate ~ 1,
      Cumulative_death_rate ~ 1,
      HPV_YEAR_INTRODUCTION ~ function(x) sprintf("%.0f", x),
      total_pop ~ 1,
      pop_density ~ 1,
      median_age ~ 1,
      pop_growth_rate ~ 1,
      fertility_rate ~ 1,
      death_rate ~ 1,
      life_expect ~ 1,
      migration ~ 1
    )
  ) %>%
  modify_header(
    stat_0 = "n/N (%), mean (sd), or median (IQR), N = {n}",
    label = "Characteristic"
  ) %>% as_tibble() %>%
  mutate(`n/N (%), mean (sd), or median (IQR), N = 100` = if_else(is.na(`n/N (%), mean (sd), or median (IQR), N = 100`), " ", `n/N (%), mean (sd), or median (IQR), N = 100`))

@@

saveRDS(table1, here("results","tables","table1.rds"))
save_as_image(as_flex_table(table1), path = here("results","tables","table1.png"))
as_flextable(table1_display)

@@

Because table rendering to Word appears broken right now, I'll split up the table and save the pieces as pictures, then insert the pictures into the manuscript document.
```{r}
#This is creating a "Table 1" for coverage and COVID burden
# Process the data and create a summary table using dplyr
coverage_covid <- c("coverage_2022", "coverage_2019", "coverage_diff", "Cumulative_case_rate", 
    "Cumulative_death_rate")
table1_cov_covid <- project_data %>%
  dplyr::select(-CODE, -CODE2, -Country, -year_covid) %>%
  dplyr::select(
    coverage_2022, coverage_2019, coverage_diff, Cumulative_case_rate, Cumulative_death_rate
  ) %>%
  tbl_summary(
    type = all_continuous() ~ "continuous2",
    statistic = list(
      all_continuous() ~ c("{mean} ({sd})", "{median} ({p25}, {p75})"),
      all_categorical() ~ "{n} / {N} ({p}%)"
    ),
    digits = list(
      coverage_2022 ~ 1,
      coverage_2019 ~ 1,
      coverage_diff ~ 1,
      Cumulative_case_rate ~ 1,
      Cumulative_death_rate ~ 1
    )
  ) %>%
  modify_header(
    stat_0 = "Mean (sd) or median (IQR), N = {n}",
    label = "Characteristic"
  ) %>% as_tibble() %>%
  mutate(`Mean (sd) or median (IQR), N = 100` = if_else(is.na(`Mean (sd) or median (IQR), N = 100`), " ", `Mean (sd) or median (IQR), N = 100`)) %>%
  gt() %>%
  tab_style(
    style = cell_text(weight = "bold"), # Bold text
    locations = cells_body(
      columns = Characteristic,
      rows = grepl(paste(word_list, collapse = "|"), Characteristic, ignore.case = TRUE)  # Apply bold if "mean" or "median" is NOT in the Variable column
    )
  )%>%
    #Making all column headers bld
    tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels(everything()) 
  ) %>%
  tab_options(
    table.font.size = px(10),        # Set font size
    data_row.padding = px(1),        # Reduce row padding
    column_labels.padding = px(2)    # Reduce padding in column headers
  )

@@

#This is creating the "Table 1" for vaccination program variables
# Process the data and create a summary table using dplyr
vac_program <- c("HPV_NATIONAL_SCHEDULE", "HPV_YEAR_INTRODUCTION", 
    "HPV_PRIM_DELIV_STRATEGY", "HPV_SEX", "doses_rec")
table1_vac_program <- project_data %>%
  dplyr::select(-CODE, -CODE2, -Country, -year_covid) %>%
  dplyr::select(
    HPV_NATIONAL_SCHEDULE, HPV_YEAR_INTRODUCTION, 
    HPV_PRIM_DELIV_STRATEGY, HPV_SEX, doses_rec
  ) %>%
  tbl_summary(
    type = all_continuous() ~ "continuous2",
    statistic = list(
      all_continuous() ~ c("{mean} ({sd})", "{median} ({p25}, {p75})"),
      all_categorical() ~ "{n} / {N} ({p}%)"
    ),
    digits = list(
      HPV_YEAR_INTRODUCTION ~ function(x) sprintf("%.0f", x)
    )
  ) %>%
  modify_header(
    stat_0 = "n/N (%), mean (sd), or median (IQR), N = {n}",
    label = "Characteristic"
  ) %>% as_tibble() %>%
  mutate(`n/N (%), mean (sd), or median (IQR), N = 100` = if_else(is.na(`n/N (%), mean (sd), or median (IQR), N = 100`), " ", `n/N (%), mean (sd), or median (IQR), N = 100`)) %>% #Replacing NA with a space so that NA doesn't get printed in the table
  gt() %>%
  tab_style(
    style = cell_text(weight = "bold"), # Bold text
    locations = cells_body(
      columns = Characteristic,
      rows = grepl(paste(word_list, collapse = "|"), Characteristic, ignore.case = TRUE)  # Apply bold if "mean" or "median" is NOT in the Variable column
    )
  )%>%
    #Making all column headers bld
    tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels(everything()) 
  ) %>%
  tab_options(
    table.font.size = px(10),        # Set font size
    data_row.padding = px(1),        # Reduce row padding
    column_labels.padding = px(2)    # Reduce padding in column headers
  )

@@

###########
#This is creating the combined table 1 that can be used to pull numbers from 
# Process the data and create a summary table using dplyr
demo_list <- c("WHO_REGION", "WB_INCOME", 
    "total_pop", "pop_density", "median_age", "pop_growth_rate", "fertility_rate", 
    "death_rate", "life_expect", "migration")
table1_demo <- project_data %>%
  dplyr::select(-CODE, -CODE2, -Country, -year_covid) %>%
  dplyr::select(
    WHO_REGION, WB_INCOME, 
    total_pop, pop_density, median_age, pop_growth_rate, fertility_rate, 
    death_rate, life_expect, migration
  ) %>%
  tbl_summary(
    type = all_continuous() ~ "continuous2",
    statistic = list(
      all_continuous() ~ c("{mean} ({sd})", "{median} ({p25}, {p75})"),
      all_categorical() ~ "{n} / {N} ({p}%)"
    ),
    digits = list(
      total_pop ~ 1,
      pop_density ~ 1,
      median_age ~ 1,
      pop_growth_rate ~ 1,
      fertility_rate ~ 1,
      death_rate ~ 1,
      life_expect ~ 1,
      migration ~ 1
    )
  ) %>%
  modify_header(
    stat_0 = "Mean (sd) or median (IQR), N = {n}",
    label = "Characteristic"
  ) %>% as_tibble() %>%
  mutate(`Mean (sd) or median (IQR), N = 100` = if_else(is.na(`Mean (sd) or median (IQR), N = 100`), " ", `Mean (sd) or median (IQR), N = 100`)) %>%
  gt() %>%
  tab_style(
    style = cell_text(weight = "bold"), # Bold text
    locations = cells_body(
      columns = Characteristic,
      rows = grepl(paste(word_list, collapse = "|"), Characteristic, ignore.case = TRUE)  # Apply bold if "mean" or "median" is NOT in the Variable column
    )
  )%>%
    #Making all column headers bld
    tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels(everything()) 
  ) %>%
  tab_options(
    table.font.size = px(8),        # Set font size
    data_row.padding = px(1),        # Reduce row padding
    column_labels.padding = px(2)    # Reduce padding in column headers
  )

@@

scatter_case_covdiff <- project_data %>%
  ggplot(aes(Cumulative_case_rate,coverage_diff)) + geom_point() + geom_smooth(method = lm) +
  labs(
    x = "Number of COVID cases in 2020-2022 per 100,000 persons",
    y = "Difference in HPV vaccination coverage between 2022 and 2019"
  ) 
scatter_case_covdiff_loc <- here("results","figures","scatter_case_covdiff.png")
# Save the last plot created as a PNG
ggsave(scatter_case_covdiff_loc, width = 8, height = 6, dpi = 300)

scatter_death_covdiff <- project_data %>%
  ggplot(aes(Cumulative_death_rate, coverage_diff)) + geom_point() + geom_smooth(method = lm) +
  labs(
    x = "Number of COVID deaths in 2020-2022 per 100,000 persons",
    y = "Difference in HPV vaccination coverage between 2022 and 2019"
  ) 
scatter_death_covdiff_loc <- here("results","figures","scatter_death_covdiff.png")
# Save the last plot created as a PNG
ggsave(scatter_death_covdiff_loc, width = 8, height = 6, dpi = 300)
```

@@

# Fit a regression tree model
reg_tree <- rpart(coverage_diff ~ total_pop + pop_density + median_age + pop_growth_rate + fertility_rate + death_rate + life_expect + migration + Cumulative_case_rate + Cumulative_death_rate + HPV_YEAR_INTRODUCTION + WHO_REGION + WB_INCOME + HPV_NATIONAL_SCHEDULE + HPV_YEAR_INTRODUCTION + HPV_PRIM_DELIV_STRATEGY + HPV_SEX + doses_rec, 
                  data = project_data, 
                  method = "anova")  # anova method for regression trees

>>>>

```{r}
#Path to data. Note the use of the here() package and not absolute paths
data_location <- here::here("data","processed-data","project_data.rds")
#load data
project_data <- readRDS(data_location)
#Restricting project_data to complete rows 
cc_project_data <- project_data %>%
  drop_na()
```

@@

```{r}
#histogram of difference in coverage
outcome_hist <- ggplot(cc_project_data, aes(x = coverage_diff)) +
  geom_histogram(binwidth = 5, fill = "skyblue", color = "black") +
  labs(
    x = "Difference in HPV vaccination coverage from 2022 to 2019",
    y = "Count"
  )

@@

#### Creating "Table 1" to show the distribution of each characteristic
```{r}
  table1 <- cc_project_data %>% dplyr::select(-CODE, -CODE2, -Country, -year_covid) %>% #Reordering the variables into the order I want displayed in the table
  dplyr::select(coverage_2022, coverage_2019, coverage_diff, Cumulative_case_rate, Cumulative_death_rate, HPV_NATIONAL_SCHEDULE, HPV_YEAR_INTRODUCTION, HPV_PRIM_DELIV_STRATEGY, HPV_SEX, doses_rec, WHO_REGION, WB_INCOME, total_pop,  total_pop, pop_density, median_age, pop_growth_rate, fertility_rate, death_rate, life_expect, migration) %>%
  tbl_summary(
    type = all_continuous() ~ "continuous2",
    statistic = list(   #Setting the statistics to calculate
      all_continuous() ~ c(
      "{mean} ({sd})",
      "{median} ({p25}, {p75})"
    ),
      all_categorical() ~ "{n} / {N} ({p}%)"),
    digits = list(   #Setting number of decimal places for each variable
      coverage_2022 ~ 1,
      coverage_2019 ~ 1,
      coverage_diff ~ 1,
      Cumulative_case_rate ~ 1,
      Cumulative_death_rate ~ 1,
      HPV_YEAR_INTRODUCTION ~ function(x) sprintf("%.0f", x),
      total_pop ~ 1,
      pop_density ~ 1,
      median_age ~ 1,
      pop_growth_rate ~ 1,
      fertility_rate ~ 1,
      death_rate ~ 1,
      life_expect ~ 1,
      migration ~ 1
    )) %>%
  modify_header(
    stat_0 = "**n/N (%), mean (SD), or median (IQR),** N = {n}") %>%
  modify_footnote(all_stat_cols() ~ NA) %>%
  modify_table_styling(
    columns = label,    # left aligning "label" column
    align = "left"
  ) 
# modify_header(stat0~ "**n/N (%), mean (sd), or median (IQR),**\n N = {n}")

@@

```{r}
#This is creating the combined table 1 that can be used to pull numbers from 
# Process the data and create a summary table using dplyr
word_list <- c("coverage_2022", "coverage_2019", "coverage_diff", "Cumulative_case_rate", 
    "Cumulative_death_rate", "HPV_NATIONAL_SCHEDULE", "HPV_YEAR_INTRODUCTION", 
    "HPV_PRIM_DELIV_STRATEGY", "HPV_SEX", "doses_rec", "WHO_REGION", "WB_INCOME", 
    "total_pop", "pop_density", "median_age", "pop_growth_rate", "fertility_rate", 
    "death_rate", "life_expect", "migration")
table1_prelim <- cc_project_data %>%
  dplyr::select(-CODE, -CODE2, -Country, -year_covid) %>%
  dplyr::select(
    coverage_2022, coverage_2019, coverage_diff, Cumulative_case_rate, 
    Cumulative_death_rate, HPV_NATIONAL_SCHEDULE, HPV_YEAR_INTRODUCTION, 
    HPV_PRIM_DELIV_STRATEGY, HPV_SEX, doses_rec, WHO_REGION, WB_INCOME, 
    total_pop, pop_density, median_age, pop_growth_rate, fertility_rate, 
    death_rate, life_expect, migration
  ) %>%
  tbl_summary(
    type = all_continuous() ~ "continuous2",
    statistic = list(
      all_continuous() ~ c("{mean} ({sd})", "{median} ({p25}, {p75})"),
      all_categorical() ~ "{n} / {N} ({p}%)"
    ),
    digits = list(
      coverage_2022 ~ 1,
      coverage_2019 ~ 1,
      coverage_diff ~ 1,
      Cumulative_case_rate ~ 1,
      Cumulative_death_rate ~ 1,
      HPV_YEAR_INTRODUCTION ~ function(x) sprintf("%.0f", x),
      total_pop ~ 1,
      pop_density ~ 1,
      median_age ~ 1,
      pop_growth_rate ~ 1,
      fertility_rate ~ 1,
      death_rate ~ 1,
      life_expect ~ 1,
      migration ~ 1
    )
  ) %>%
  modify_header(
    stat_0 = "n/N (%), mean (SD), or median (IQR), N = {n}",
    label = "Characteristic"
  ) %>% as_tibble() %>%
  mutate(`n/N (%), mean (SD), or median (IQR), N = 98` = if_else(is.na(`n/N (%), mean (SD), or median (IQR), N = 98`), " ", `n/N (%), mean (SD), or median (IQR), N = 98`))

@@

saveRDS(table1, here("results","tables","table1.rds"))
#save_as_image(as_flex_table(table1), path = #here("results","tables","table1.png"))
#as_flextable(table1_display)

@@

Because table rendering to Word appears broken right now, I'll split up the table and save the pieces as pictures, then insert the pictures into the manuscript document.
```{r}
#This is creating a "Table 1" for coverage and COVID burden
# Process the data and create a summary table using dplyr
coverage_covid <- c("coverage_2022", "coverage_2019", "coverage_diff", "Cumulative_case_rate", 
    "Cumulative_death_rate")
table1_cov_covid <- cc_project_data %>%
  dplyr::select(-CODE, -CODE2, -Country, -year_covid) %>%
  dplyr::select(
    coverage_2022, coverage_2019, coverage_diff, Cumulative_case_rate, Cumulative_death_rate
  ) %>%
  tbl_summary(
    type = all_continuous() ~ "continuous2",
    statistic = list(
      all_continuous() ~ c("{mean} ({sd})", "{median} ({p25}, {p75})"),
      all_categorical() ~ "{n} / {N} ({p}%)"
    ),
    digits = list(
      coverage_2022 ~ 1,
      coverage_2019 ~ 1,
      coverage_diff ~ 1,
      Cumulative_case_rate ~ 1,
      Cumulative_death_rate ~ 1
    )
  ) %>%
  modify_header(
    stat_0 = "Mean (SD) or median (IQR), N = {n}",
    label = "Characteristic"
  ) %>% as_tibble() %>%
  mutate(`Mean (SD) or median (IQR), N = 98` = if_else(is.na(`Mean (SD) or median (IQR), N = 98`), " ", `Mean (SD) or median (IQR), N = 98`)) %>%
  gt() %>%
  tab_style(
    style = cell_text(weight = "bold"), # Bold text
    locations = cells_body(
      columns = Characteristic,
      rows = grepl(paste(word_list, collapse = "|"), Characteristic, ignore.case = TRUE)  # Apply bold if "mean" or "median" is NOT in the Variable column
    )
  )%>%
    #Making all column headers bld
    tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels(everything()) 
  ) %>%
  tab_options(
    table.font.size = px(10),        # Set font size
    data_row.padding = px(1),        # Reduce row padding
    column_labels.padding = px(2)    # Reduce padding in column headers
  )  %>% 
  text_case_match(
    "coverage_2022" ~ "2022 HPV vaccination coverage",
    "coverage_2019" ~ "2019 HPV vaccination coverage",
    "coverage_diff" ~ "Coverage difference between 2022 and 2019",
    "Cumulative_case_rate" ~ "Cumulative COVID cases",
    "Cumulative_death_rate" ~ "Cumulative COVID deaths"
  )

@@

#This is creating the "Table 1" for vaccination program variables
# Process the data and create a summary table using dplyr
vac_program <- c("HPV_NATIONAL_SCHEDULE", "HPV_YEAR_INTRODUCTION", 
    "HPV_PRIM_DELIV_STRATEGY", "HPV_SEX", "doses_rec")
table1_vac_program <- cc_project_data %>%
  dplyr::select(-CODE, -CODE2, -Country, -year_covid) %>%
  dplyr::select(
    HPV_NATIONAL_SCHEDULE, HPV_YEAR_INTRODUCTION, 
    HPV_PRIM_DELIV_STRATEGY, HPV_SEX, doses_rec
  ) %>%
  tbl_summary(
    type = all_continuous() ~ "continuous2",
    statistic = list(
      all_continuous() ~ c("{mean} ({sd})", "{median} ({p25}, {p75})"),
      all_categorical() ~ "{n} / {N} ({p}%)"
    ),
    digits = list(
      HPV_YEAR_INTRODUCTION ~ function(x) sprintf("%.0f", x)
    )
  ) %>%
  modify_header(
    stat_0 = "n/N (%), mean (SD), or median (IQR), N = {n}",
    label = "Characteristic"
  ) %>% as_tibble() %>%
  mutate(`n/N (%), mean (SD), or median (IQR), N = 98` = if_else(is.na(`n/N (%), mean (SD), or median (IQR), N = 98`), " ", `n/N (%), mean (SD), or median (IQR), N = 98`)) %>% #Replacing NA with a space so that NA doesn't get printed in the table
  gt() %>%
  tab_style(
    style = cell_text(weight = "bold"), # Bold text
    locations = cells_body(
      columns = Characteristic,
      rows = grepl(paste(word_list, collapse = "|"), Characteristic, ignore.case = TRUE)  # Apply bold if "mean" or "median" is NOT in the Variable column
    )
  )%>%
    #Making all column headers bld
    tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels(everything()) 
  ) %>%
  tab_options(
    table.font.size = px(10),        # Set font size
    data_row.padding = px(1),        # Reduce row padding
    column_labels.padding = px(2)    # Reduce padding in column headers
  ) %>% 
  text_case_match(
    "HPV_NATIONAL_SCHEDULE" ~ "National HPV vaccination schedule",
    "HPV_YEAR_INTRODUCTION" ~ "Year of HPV vaccine introduction",
    "HPV_PRIM_DELIV_STRATEGY" ~ "Primary vaccine delivery strategy",
    "HPV_SEX" ~ "Genders vaccinated",
    "doses_rec" ~ "Number of recommended doses"
  )

@@

###########
#This is creating the sociodemographics table for printing
# Process the data and create a summary table using dplyr
demo_list <- c("WHO_REGION", "WB_INCOME", 
    "total_pop", "pop_density", "median_age", "pop_growth_rate", "fertility_rate", 
    "death_rate", "life_expect", "migration")
table1_demo <- cc_project_data %>%
  dplyr::select(-CODE, -CODE2, -Country, -year_covid) %>%
  dplyr::select(
    WHO_REGION, WB_INCOME, 
    total_pop, pop_density, median_age, pop_growth_rate, fertility_rate, 
    death_rate, life_expect, migration
  ) %>%
  tbl_summary(
    type = all_continuous() ~ "continuous2",
    statistic = list(
      all_continuous() ~ c("{mean} ({sd})", "{median} ({p25}, {p75})"),
      all_categorical() ~ "{n} / {N} ({p}%)"
    ),
    digits = list(
      total_pop ~ 1,
      pop_density ~ 1,
      median_age ~ 1,
      pop_growth_rate ~ 1,
      fertility_rate ~ 1,
      death_rate ~ 1,
      life_expect ~ 1,
      migration ~ 1
    )
  ) %>%
  modify_header(
    stat_0 = "Mean (SD) or median (IQR), N = {n}",
    label = "Characteristic"
  ) %>% as_tibble() %>%
  mutate(`Mean (SD) or median (IQR), N = 98` = if_else(is.na(`Mean (SD) or median (IQR), N = 98`), " ", `Mean (SD) or median (IQR), N = 98`)) %>%
  gt() %>%
  tab_style(
    style = cell_text(weight = "bold"), # Bold text
    locations = cells_body(
      columns = Characteristic,
      rows = grepl(paste(word_list, collapse = "|"), Characteristic, ignore.case = TRUE)  # Apply bold if "mean" or "median" is NOT in the Variable column
    )
  )%>%
    #Making all column headers bld
    tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels(everything()) 
  ) %>%
  tab_options(
    table.font.size = px(8),        # Set font size
    data_row.padding = px(1),        # Reduce row padding
    column_labels.padding = px(2)    # Reduce padding in column headers
  ) %>% 
  text_case_match(
    "WHO_REGION" ~ "WHO region",
    "AFR" ~ "African region",
    "AMR" ~ "Region of the Americas",
    "EMR" ~ "Eastern Mediterranean region",
    "EUR" ~ "European region",
    "SEAR" ~ "South-East Asian region",
    "WPR" ~ "Western Pacific region",
    "WB_INCOME" ~ "World Bank income level",
    "total_pop" ~ "Total population (thousands)",
    "pop_density" ~ "Population density (persons per square km)",
    "median_age" ~ "Median age",
    "pop_growth_rate" ~ "Population growth rate (%)",
    "fertility_rate" ~ "Total fertility rate (live births/woman)",
    "death_rate" ~ "Crude death rate (deaths per 1000 people)",
    "life_expect" ~ "Life expectancy at birth (years)",
    "migration" ~ "Net migration rate (per 1000 people)"
  )

@@

scatter_case_covdiff <- cc_project_data %>%
  ggplot(aes(Cumulative_case_rate,coverage_diff)) + geom_point() + geom_smooth(method = lm) +
  labs(
    x = "Cumulative number of COVID cases in 2020-2022 per 100,000 persons",
    y = "Difference in HPV vaccination coverage between 2022 and 2019"
  ) 
scatter_case_covdiff_loc <- here("results","figures","scatter_case_covdiff.png")
# Save the last plot created as a PNG
ggsave(scatter_case_covdiff_loc, width = 8, height = 6, dpi = 300)

scatter_death_covdiff <- cc_project_data %>%
  ggplot(aes(Cumulative_death_rate, coverage_diff)) + geom_point() + geom_smooth(method = lm) +
  labs(
    x = "Number of COVID deaths in 2020-2022 per 100,000 persons",
    y = "Difference in HPV vaccination coverage between 2022 and 2019"
  ) 
scatter_death_covdiff_loc <- here("results","figures","scatter_death_covdiff.png")
# Save the last plot created as a PNG
ggsave(scatter_death_covdiff_loc, width = 8, height = 6, dpi = 300)
```

#### Creating bivariate plots for demographics and the outcome
```{r}

#Violin plots of the outcome by each categorical variable
demo1 <- cc_project_data %>%
  ggplot(aes(coverage_diff, WHO_REGION)) + geom_violin() + labs(x = "Difference in vaccination coverage", y = "WHO region")

demo2 <- cc_project_data %>%
  ggplot(aes(coverage_diff, WB_INCOME)) + geom_violin() + labs(x = "Difference in vaccination coverage", y = "Country income level")

demo3 <- cc_project_data %>%
  ggplot(aes(coverage_diff, total_pop)) + geom_point() + geom_smooth() + labs(x = "Difference in vaccination coverage", y = "Total population (in thousands)")

demo4 <- cc_project_data %>%
  ggplot(aes(coverage_diff, pop_density)) + geom_point() + geom_smooth() + labs(x = "Difference in vaccination coverage", y = "Population density (persons per square km)")

#Building 4 panel figure of country demographics
bivar_demo_1 <- (demo1 | demo2) / (demo3 | demo4)
bivar_demo_1_loc <- here("results","figures","bivar_demo_1.png")
# Save the plot created as a PNG
ggsave(bivar_demo_1_loc, plot = bivar_demo_1, width = 8, height = 6, dpi = 300)

demo5 <- cc_project_data %>%
  ggplot(aes(coverage_diff, median_age)) + geom_point() + geom_smooth() + labs(x = "Difference in vaccination coverage", y = "Median age of population")

demo6 <- cc_project_data %>%
  ggplot(aes(coverage_diff, fertility_rate)) + geom_point() + geom_smooth() + labs(x = "Difference in vaccination coverage", y = "Fertility rate (live births per woman)")

demo7 <- cc_project_data %>%
  ggplot(aes(coverage_diff, death_rate)) + geom_point() + geom_smooth() + labs(x = "Difference in vaccination coverage", y = "Death rate (deaths per 1,000 population)")

demo8 <- cc_project_data %>%
  ggplot(aes(coverage_diff, life_expect)) + geom_point() + geom_smooth() + labs(x = "Difference in vaccination coverage", y = "Life expectancy (in years)")

demo9 <- cc_project_data %>%
  ggplot(aes(coverage_diff, migration)) + geom_point() + geom_smooth() + labs(x = "Difference in vaccination coverage", y = "Migration rate (per 1000 population)")

#Building 5 panel figure of the rest of the demographics
bivar_demo_2 <- (demo5 | demo6 | demo7) / (demo8 | demo9)
bivar_demo_2_loc <- here("results","figures","bivar_demo_2.png")
# Save the plot created as a PNG
ggsave(bivar_demo_2_loc, plot = bivar_demo_2, width = 8, height = 6, dpi = 300)

#Building 9 panel demographic figure
demo_fig_loc <- here("results","figures","demo_fig.png")
demo_fig <- (demo1 | demo2 | demo3) / (demo4 | demo5 | demo6) / (demo7 | demo8 | demo9) 
ggsave(demo_fig_loc, plot = demo_fig, width = 8, height = 10, dpi = 300)

#Vaccination variables
vac1 <- cc_project_data %>%
  ggplot(aes(coverage_diff, HPV_NATIONAL_SCHEDULE)) + geom_violin() + labs(x = "Difference in vaccination coverage", y = "National vaccine schedule")

vac2 <- cc_project_data %>%
  ggplot(aes(coverage_diff, HPV_PRIM_DELIV_STRATEGY)) + geom_violin() + labs(x = "Difference in vaccination coverage", y = "Primary vaccination delivery strategy")

vac3 <- cc_project_data %>%
  ggplot(aes(coverage_diff, HPV_SEX)) + geom_violin() + labs(x = "Difference in vaccination coverage", y = "Genders vaccinated")

vac4 <- cc_project_data %>%
  ggplot(aes(coverage_diff, as.factor(doses_rec))) + geom_violin() + labs(x = "Difference in vaccination coverage", y = "Number of recommended doses")

vac5 <- cc_project_data %>%
  ggplot(aes(coverage_diff, HPV_YEAR_INTRODUCTION)) + geom_point() + geom_smooth() + labs(x = "Difference in vaccination coverage", y = "Year of vaccine introduction")

#Building 5 panel figure of vaccination program variables
bivar_vac <- (vac1 | vac2 | vac3) / (vac4 | vac5)
bivar_vac_loc <- here("results","figures","bivar_vac.png")
# Save the plot created as a PNG
ggsave(bivar_vac_loc, plot = bivar_vac, width = 8, height = 6, dpi = 300)
```

@@

# Fit a regression tree model
reg_tree <- rpart(coverage_diff ~ total_pop + pop_density + median_age + pop_growth_rate + fertility_rate + death_rate + life_expect + migration + Cumulative_case_rate + Cumulative_death_rate + HPV_YEAR_INTRODUCTION + WHO_REGION + WB_INCOME + HPV_NATIONAL_SCHEDULE + HPV_YEAR_INTRODUCTION + HPV_PRIM_DELIV_STRATEGY + HPV_SEX + doses_rec, 
                  data = cc_project_data, 
                  method = "anova")  # anova method for regression trees
